Papers

### 2024-04-14 quarto/index.qmd
update

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models (Llama).
Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
studying language and multimodal models.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.

@@

[Filled, see you next year] *If you are interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> on LLMs with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*

>>>>

**Aston Zhang** is a research scientist at the <a href="https://llama.meta.com/" target="_blank">Llama</a> team of Meta Generative AI, building large language models.
Prior to this, he was a scientist/manager at Amazon Web Services AI Research.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.

@@

##### News

* *If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.* [Filled, see you next year]
